### 2021-07-21 doc/thesis/chapters/hls.tex
workflow wip

see Chapter "Software Verification and Vivado HLS" of \cite{VivadoUgHLSIntro}

- recommended to use software verification tools, like valgrind or Coverity (dynamic code checker)\\
- use code coverage with e.g. gcov for testbench

general workflow:
- develop c/c++\\
- verify it using above mentioned software tools \\
- HLS testbench it (c-sim)\\
- transform to RTL\\
- HLS testbench it (co-sim)\\
- integrate the generated RTL to a larger FPGA design\\
- synthesize FPGA bitstream\\
- use on FPGA\\

>>>>

This section describes the workflow for Xilinx HLS, as it is recommended in the user guide \textit{Introduction to FPGA Design with Vivado High-Level Synthesis} \cite{VivadoUgHLSIntro}.\\

Generally, as the user guide states, the quality and the correctness of the generated output can only be as good as its input.
Consequently, it is very important to follow the design recommendations and adhere to specific rules in order to produce a high-quality input software.\\

The following list presents the main steps that are required in the implementation workflow of an HLS IP core project.\\

\begin{itemize}
  \item \textbf{Software Testbench}\\
      The developed HLS IP code needs to be verified and checked for correct functionality in a software testbench, before it gets processed to RTL code.
      This can be done by using using conventional software development tools.
      Xilinx specifically recommends dynamic code checker tools like \textit{valgrind} or \textit{Coverity}.
      They support a developer in finding memory leaks, out-of-bounds memory access, uninitialized variables and similar issues.
      Furthermore, the application of code coverage tools like \textit{gcov} is recommended as well.
      In that way, the percentage of executed code lines of testbench and HLS code can be measured, to ensure a sufficient level of testing.
      The software testbench is also called 'C Simulation'.\\

      The implementation of the HLS IP code is subject to restrictions.
      As an example, dynamic memory allocation is not supported, since the entire code must be analyzable at runtime to be processed into RTL code.
      %For further details, please read the user guides regarding Xilinx HLS.
      In contrast, the testbench code does not have any restrictions.
      Anything that is supported in C/\cplusplus\ may be used here.\\

  \item \textbf{Co-Simulation}\\
      Co-Simulation serves the purpose verify the correct functionality of the generated RTL code.
      However, the main goal is not to verify the algorithm here.
      This is already done by above described C simulation.

  \item \textbf{integrate the generated RTL to a larger FPGA design}\\
  \item \textbf{synthesize FPGA bitstream}\\
  \item \textbf{use on FPGA}\\
\end{itemize}
